On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-09 Manuscript/reply.tex
further comments and edits

Thank you for this idea. We have reformatted all of our coverage rate plots 
accordingly, which has saved a lot of space!

\jy{Lets use the new graph in the paper too. You may also use
  different line types to distinguish them.}
\mc{addressed}

\jy{Use latex symbols for mu, sigma, phi in the plots.}
\mc{for exponential, the first-order autocorrelation coefficient
is not the same as $\phi$, should I define $\rho$ as the first-order 
autocorrelation coefficient in the manuscript so that I can use the greek letter
in the plot}

@@

\eds{I also added subsubsections (paragraphs) for the Normal and Exponential 
Marginal Distributions under Design and Results subsections.
Is it possible to put to make the [Simulation Study] Design and 
[Simulation Study] Results as two separate 
sections instead of placing each as subsections of the Simulation Study section,
or does the journal formatting prohibit this?  If you can change this, then the 
Normal and Exponential Marginal subsubsections can be updated to subsections
under the Simulation Study Design and Simulation Study Results sections.}  
\mc{addressed}

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect percentile-based CIs (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
under
non-normal error structures. We have called attention to this in the Exponential
Marginal Distribution subsection of the Design section.

\eds{you will need to add more here.  This concerns the
(asymptotic) distribution of the statistics, not the underlying error 
structure.}
\mc{I changed it a bit... I'm not sure what to say for circumstances in which
“non-parametric” CI 
formulas would work better}

>>>>

Thank you for the suggestion idea. We have reformatted all of our coverage rate plots 
accordingly, which has saved a lot of space!

\mc{for exponential, the first-order autocorrelation coefficient
is not the same as $\phi$, should I define $\rho$ as the first-order 
autocorrelation coefficient in the manuscript so that I can use the greek letter
in the plot}
\jy{Yes.}

@@

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the point estimator. This asymptotic
distribution depends more on the sample size than on the marginal
distribution of the time series. So we expect such CIs to 
have similar performance for different marginal distributions when the
sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
Recentered Percentile CI) are not necessatily expected to perform
better under non-normal marginal distributions. The student's t and
and normal-based CIs are only noticeably different when the number of
blocks is smaller than 20. We have added a discussion on this point in
the first paragraph of the subsection of Marginal Unit Exponential
Distribution.
